First Draft

### 2021-05-05 draft.Rmd
methods decided

```{r}
# Packages
library(ggplot)
library(plotly)
library(dplyr)
library(tidyverse)
library(caret)
```

# Question

# Exploratory Data Analysis

@@

# Fairness Assessment

# Conclusions

# Future Work

>>>>

```{r}
# Packages
library(ggplot2)
library(plotly)
library(dplyr)
library(tidyverse)
library(caret)
```

```{r}
# bring in the data
stroke = read_csv("stroke.csv")
```

# Question
•	Question and background information on the data and why you are asking this question(s).  References to previous research/evidence generally would be nice to include. – You must present your question to me during office hours, either next week on  26th or the following week on the 3rd

# Exploratory Data Analysis
•	Exploratory Data Analysis – Initial summary statistics and graphs with an emphasis on variables you believe to be important for your analysis.

@@

•	Methods – Techniques you are using to address your question and the results of those methods.
•	Evaluation of your model – Select appropriate metrics and explain the output as it relates to your question.

## KNN

## Clustering

## Decision

## Random Forest

# Fairness Assessment
•	Fairness assessment – if necessary, should you happen to have any protected classes.

# Conclusions
•	Conclusions – What can you say about the results of the methods section as it relates to your question given the limitations to your model.

# Future Work
•	Future work – What additional analysis is needed or what limited your analysis on this project.
